\section{Data Sources for IPv6 Deployment Measurements}

\subsection{BGP Route Data}

The first source of IPv6 data we shall examine is Border Gateway Protocol(BGP)
Route data. BGP is the routing protocol used to route traffic across the backbone
of the internet, between the individual networks (known as Autonomous
Systems (ASs)) that make up the internet. Each router that is part of this core
internetwork holds a complete view of the entire

IPv6 traffic
is routed across the internet using 

\subsection{Prefix Allocation Data}

\subsection{Usage Data}

\subsection{Active Measurements}

\begin{itemize}
    \item BGP Route Data
    \begin{itemize}
        \item sources
        \item analysis of data
        \begin{itemize}
            \item What has been done?
            \item How can we do this?
        \end{itemize}
        \item difficulties and potential problems with the date
    \end{itemize}
    \item Prefix Allocation
    \begin{itemize}
        \item same specifics as BGP Routes
        \item PI vs. PA space, can we measure this?
        \item can relate allocation to use?
    \end{itemize}
    \item Usage Data
    \begin{itemize}
        \item same specifics as BGP Routes
        \item can we measure the extent of tunneling?
        \item happy eyeballs
        \item browser configuration (re: dual stack)
    \end{itemize}
    \item Active Measurements
    \begin{itemize}
        \item same specifics as BGP Routes
        \item Atlas and Ark
        \item how does this add to the existing other data sets?
    \end{itemize}
\end{itemize}
